---
title: "Cluster Analysis"
author: "Jack R. O'Connor" 
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, results='hide'}
# Loading Data
pitch <- read.csv("/Users/Jacksmac/Desktop/IST 707 Project/Project Data.csv", na.strings = "NA")
str(pitch)

# Looking for NA values

sapply(pitch, function(x) {sum(is.na(x))})

## Removing NA Columns  
pitch.new <- pitch[ , -c(11,12,13,14,40,41,43)]
```

Subsetting with release speed, release spin rate, realse pos x and z, pfx_x, pfx_z, plate_x, plate_z

Will add in zone and pitch type later
```{r}
pitch.cluster.data <- pitch.new[ , c(1, 11, 3,  4,  5, 24, 25, 26, 27, 50)]
str(pitch.cluster.data)
```

Removing NA values
```{r}
pitch.cluster.data <- na.omit(pitch.cluster.data)
```

Everything is factored. Unfactoring everything 
```{r}
p <- apply(pitch.cluster.data, 2, function(x) {as.numeric(as.character(x))}) 
str(p)
cluster.pitch <- as.data.frame(p)
str(cluster.pitch)
```

Standardizing the data except zone
```{r}
# Standardize function
standardize.fun <- function(x) 
{
  std <- sd(x, na.rm = TRUE)
  mu <- mean(x, na.rm = TRUE)
  return((x-mu)/std)
}

pitch.cluster.standard <- as.data.frame(round(apply(cluster.pitch, 2, standardize.fun), 4))
str(pitch.cluster.standard)
```

Adding in pitch_type and zone

```{r}
pitch.cluster.standard$pitch_type <- pitch.cluster.data$pitch_type
pitch.cluster.standard$zone <- pitch.cluster.data$zone
str(pitch.cluster.standard)

pitch.cluster.standard <- na.omit(pitch.cluster.standard)
```

Writing the csv file for Weka Analysis
```{r}
write.csv(pitch.cluster.standard, file = "pitch.cluster.standard.csv", sep = ",")
```



Optimal number of clusters 
```{r}
k.max <- 10
wss <- sapply(1:k.max, function(k){kmeans(pitch.cluster.standard[ , -c(1:2)], k, nstart = 50, iter.max = 20)$tot.withinss})
wss

plot(1:k.max, wss, type = "b")
```

For this analysis, either 5 or 6 clusters will work based on the above chart. It looks like 6 clusters is where the graph really starts to level off. 






